Estimation of flow trajectories in a multi-lines network

### 2023-02-11 latex_files/applied_network_science_article/article_v0.tex
writing two paragraphs in the intro

\section{Introduction}

@@

This constancy entails the following Markovian behaviour for flows: let $m_{st}$ be the number of travelers embarking at stop $s$ and still inside the bus at stop $t>s$, and let $\rho_{st}$ the probability that travelers embarking at $s$ will disembark at $t$. By (\ref{nosignle}), 
\begin{displaymath}
m_{st}=\sum_{u\ge t}n_{su}=c_s \sum_{u\ge t} I(s<u)\, d_u =c_s (d_t+D_t) 
\end{displaymath}
The empirical estimate of $\rho_{st}$ is given by the proportion, among the travelers embarking at $s$ and 
 still present at $t>s$,  of travelers disembarking at $t$, that is 
\begin{displaymath}
\rho_{st}=\frac{n_{st}}{m_{st}}=\frac{c_s\,  d_t}{c_s\,  (d_t+D_t)}=\frac{d_t}{d_t+D_t}=\frac{b_t}{C_t\, (d_t+D_t)}\le 1
\end{displaymath}
which depends on $t$ only: it  finally  turns out that the disembarkment probability $\rho_t=\frac{d_t}{d_t+D_t}$ at $t$ is {\em independent} of the embarkment stop $s$. Said otherwise, a traveler embarking at any stop $s$ (and thus necessarily in the bus at $F(s)=s+1$) experiences the {\em same disembarkment probability} at each  stop $t$.

>>>>

\section{Introduction}
Transportation networks determine our mobility, require a considerable amount of planning and resources, and elicit much hopes and critics. 
They also constitute an endless source of inspiration in formal modeling and optimization, as attested in operations research (classical optimal transportation, maximum flow problem), quantitative geography and spatial econometrics (spatial navigation, multimodality, gravity models for flows), and machine learning (recent developments in regularized optimal transportation, such as color transfer or images interpolation; see e.g. \cite{peyre2019computational}).

This contribution adresses a simple, yet central issue in public transportation networks: given a network made of many bus lines, how can one estimate the real trips made by the travelers, on the sole basis of  the embarkment and disembarkment counts for each bus stop? Transfer of travelers between bus lines constitute the missing information, and their defendable evaluation requests some methodological reflexion and experimentation.

***

@@

This constancy entails the following Markovian behaviour for flows: let $m_{st}$ be the number of travelers embarking at stop $s$ and still inside the bus at stop $t>s$, and let $\rho_{st}$ the probability that travelers embarking at $s$ will disembark at $t$. By (\ref{nosignle}), 
\begin{displaymath}
m_{st}=\sum_{u\ge t}n_{su}=c_s \sum_{u\ge t} I(s<u)\, d_u =c_s (d_t+D_t) 
\end{displaymath}
The empirical estimate of $\rho_{st}$ is given by the proportion, among the travelers embarking at $s$ and 
 still present at $t>s$,  of travelers disembarking at $t$, that is 
\begin{displaymath}
\rho_{st}=\frac{n_{st}}{m_{st}}=\frac{c_s\,  d_t}{c_s\,  (d_t+D_t)}=\frac{d_t}{d_t+D_t}=\frac{b_t}{C_t\, (d_t+D_t)}\le 1
\end{displaymath}
which depends on $t$ only: it appears that the disembarkment probability $\rho_t=\frac{d_t}{d_t+D_t}$ at $t$ is {\em independent} of the embarkment stop $s$. Said otherwise, a traveler embarking at any stop $s$ (and thus necessarily in the bus at $F(s)=s+1$) experiences the {\em same disembarkment probability} at each further stop $t>s$.
